---
title: "dataCleaning"
author: "Margaret Bassney"
date: "2/24/2022"
output: html_document
---

```{r}
# import libraries
library(tidyverse)
library(psych)
library(lubridate)
```

```{r}
# import dataset
dat <- read.csv("TeleCom_Dyad_premeasures.csv")

head(dat)
```

```{r}
# selecting the variables we need
dat <- dat %>%
  select(dyadID, partnum, gender, religion, birthday, sexualor, race, RecordedDate, relation_length, indinc, wfh, starts_with("housework_"), starts_with("grbs_"))

head(dat)
```

# Renaming/recoding/cleaning 
```{r}
# selecting heterosexual couples only
dat<-filter(dat, sexualor=="Heterosexual")

# calculate relationship length
dat <- dat %>% 
  mutate(survey_date = as.Date("2020-08-01")) %>% 
  mutate(relation_start = as.Date(relation_length, format= "%m/%d/%y")) %>% 
  mutate(relation_days = ifelse(dyadID != 33094797, survey_date - relation_start, 2332)) %>%
  mutate(relation_yrs = relation_days / 365) 

# Recode Gender Man=0, Woman=1
dat$gender<-recode(dat$gender,"Man"=0, "Woman"=1)

# Recode Work From Home Yes=0, No=1
dat$wfh<-recode(dat$wfh, "Yes"=0, "No"=1)

# rename birthday > age 
names(dat)[names(dat) == "birthday"] <- "age"

# make partnum shorter > just 1 or 2 
dat <- dat %>%
  mutate(partnum = (sub("qual2599-0604TeleCommute_p", "", partnum)))
head(dat)


#removing some of the participants 
remove<-c(13, 132, 173, 222, 267, 274, 331, 102, 103, 165, 166, 188, 189, 291, 292, 313, 314, 319,320, 329,330)
dat<-dat[-remove,]
```

```{r}
# re-coding housework to be numbers 
dat$housework_1<-recode(dat$housework_1, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_2<-recode(dat$housework_2, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_3<-recode(dat$housework_3, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_4<-recode(dat$housework_4, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_5<-recode(dat$housework_5, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_6<-recode(dat$housework_6, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_7<-recode(dat$housework_7, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_8<-recode(dat$housework_8, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_9<-recode(dat$housework_9, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_10<-recode(dat$housework_10, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_11<-recode(dat$housework_11, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_12<-recode(dat$housework_12, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_13<-recode(dat$housework_13, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_14<-recode(dat$housework_14, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
```

```{r}
# re-coding gender role beliefs 
dat$grbs_1<-recode(dat$grbs_1, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_2<-recode(dat$grbs_2, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_3<-recode(dat$grbs_3, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_4<-recode(dat$grbs_4, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_5<-recode(dat$grbs_5, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_6<-recode(dat$grbs_6, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_7<-recode(dat$grbs_7, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_8<-recode(dat$grbs_8, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_9<-recode(dat$grbs_9, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_10<-recode(dat$grbs_10, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_11<-recode(dat$grbs_11, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_12<-recode(dat$grbs_12, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_13<-recode(dat$grbs_13, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_14<-recode(dat$grbs_14, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_15<-recode(dat$grbs_15, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_16<-recode(dat$grbs_16, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_17<-recode(dat$grbs_17, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_18<-recode(dat$grbs_18, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_19<-recode(dat$grbs_19, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_20<-recode(dat$grbs_20, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
```

```{r}
# re-coding housework_satisfied
dat$housework_satisfied<-recode(dat$housework_satisfied, "Very dissatisfied" = 1, "Somewhat dissatisfied" = 2, "Neither satisfied nor dissatisfied" = 3, "Somewhat satisfied" = 4, "Very satisfied" = 5)
```

```{r}
# re-coding housework fairness
dat$housework_fair<-recode(dat$housework_fair, "Fair to both you and your partner"=3, "Slightly unfair to you"=4, 
                           "Very fair to me"=1, "Pretty much fair to me"=2, "Very unfair to you"=5)
```


#HOUSEWORK 
##Correlation matrices
```{r}
# Correlation housework
corr.test(select(dat, housework_1, housework_2, housework_3, housework_4, 
                 housework_5, housework_6, housework_7, housework_8, housework_9, 
                 housework_10, housework_11, housework_12, housework_13, housework_14))$r
```
We can see that there are negative correlations. > type of chore= male/female 

5=Take out garbage, recycling
6=Outdoor work (yard work, rake, mow, shovel snow, garden)  
10=Upkeep of car including repairs, washing and vacuuming  
11=Small repairs around the house

```{r}
# Correlation divided by housework type (typically female vs. typically male)
corr.test(select(dat, housework_1, housework_2, housework_3, housework_4, 
                 housework_7, housework_8, housework_9, 
                 housework_12, housework_13, housework_14))$r

corr.test(select(dat, housework_5, housework_6, 
                 housework_10, housework_11))$r
```

##Average of housework devided by type of housework 
```{r}
# Average of each housework_type
dat <- dat %>%
  mutate(avg_housework_female = rowMeans(select(dat,housework_1, housework_2, housework_3, housework_4, housework_7, housework_8, housework_9, housework_12, housework_13, housework_14),na.rm = TRUE))

dat <- dat %>%
  mutate(avg_housework_male = rowMeans(select(dat, housework_5, housework_6, housework_10, housework_11),na.rm = TRUE))
head(dat)
```

#GENDER ROLE BELIEFS 
```{r}
# Correlation grbs
corr.test(select(dat, grbs_1, grbs_2,grbs_3,grbs_4,grbs_5,grbs_6,grbs_7,grbs_8,
                 grbs_9, grbs_10, grbs_11, grbs_12, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17, grbs_18, grbs_19, grbs_20))$r
```
We should check for reversed items!! 2y 3y 7 10 12 17


# Reverse score GRBS

# reverse score anything
max + min for a scale and subtract the original score from that.

```{r}
dat_reverse <- dat %>% mutate(grbs_2.r = (1 + 5) - grbs_2,
                              grbs_3.r = (1 + 5) - grbs_3,
                              grbs_7.r = (1 + 5) - grbs_7,
                              grbs_10.r = (1 + 5) - grbs_10,
                              grbs_12.r = (1 + 5) - grbs_12,
                              grbs_17.r = (1 + 5) - grbs_17)
```


```{r}
# Correlation grbs
corr.test(select(dat_reverse, grbs_1, grbs_2.r,grbs_3.r,grbs_4,grbs_5,grbs_6,grbs_7.r,grbs_8,
                 grbs_9, grbs_10.r, grbs_11, grbs_12.r, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17.r, grbs_18, grbs_19, grbs_20))$r
```

```{r}
# average grbs
dat_reverse <- dat_reverse %>%
  mutate(avg_grbs = rowMeans(select(dat_reverse, grbs_1, grbs_2.r,grbs_3.r,grbs_4,grbs_5,grbs_6,grbs_7.r,grbs_8,
                 grbs_9, grbs_10.r, grbs_11, grbs_12.r, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17.r, grbs_18, grbs_19, grbs_20),na.rm = TRUE))
head(dat_reverse)
```

#Create new dataset 
```{r}
# overall dataset with means
overall_data <- dat_reverse %>%
  select(dyadID, gender, religion, avg_housework_male, avg_housework_female, avg_grbs, housework_fair, housework_satisfied)

show(overall_data)
```

#preparing the dataset... 
```{r}
#people that are "alone": 1213424, 29196654, 29457967, 29679706, 31455950, 31822775, 33696006
#other critical ones we should exclude/check: 33728504, 29675494 & 29725200 (the other way around)
#wrong partnums: 737834
#maybe we should take the gender variable and create a new partnum variable so it is the same 

#removing the ones that have no partner (first half), #even though we already tried to remove same-sex couples, there were still some in the dataset (second half from102)
#remove<-c(13, 132, 173, 222, 267, 274, 331, 102, 103, 165, 166, 188, 189, 291, 292, 313, 314, 319,320, 329,330)
#overall_data_clean<-overall_data[-remove,]

#create another partnum var with gender 
overall_data_clean$partnum2 <- overall_data_clean$gender
head(overall_data_clean)
overall_data_clean$partnum2<-recode(overall_data_clean$partnum2, "0"=2, "1"=1)
head(overall_data)

overall_data_small <- overall_data_clean %>%
  select(dyadID, gender, avg_housework_female)


#this would be the code to get the csv file to upload to the shiny app 
write.csv(overall_data_clean2,"predyaddata.csv")
```


#Dyadic structure 

```{r}
library(tidyverse)
library(nlme)
library(mosaic)
head(overall_data)
tempA <- overall_data_clean %>%
  mutate(genderE = gender, partnum2 = 1,
          gender = ifelse (gender == 0, "A", "P")) %>%
   gather(variable, value, religion:genderE) %>%
   unite(var_ap, variable, gender) %>%
   spread(var_ap, value)
head(tempA)

#problem: Each row of output must be identified by a unique combination of keys. Keys are shared for 24 rows:
#we should look for weird things in the data 

tempB <- overall_data_clean %>%
   mutate(genderE = gender, partnum2 = 2,
          gender = ifelse(gender == 0, "P", "A")) %>%
   gather(variable, value, religion:genderE)%>%
   unite(var_ap, variable, gender) %>%
   spread(var_ap, value)
 overall_data_pair <- bind_rows(tempA, tempB) %>%
   arrange(dyadID)
 overall_data_pair
 
# acitelli_pair <- bind_rows(tempA, tempB) %>%
#  mutate(genderstring_A = ifelse(genderE_A == 1, "Husband", "Wife")) %>%
#  arrange(cuplid) 
#
 rm(tempA, tempB)
 head(overall_data_pair)
```

