---
title: "dataCleaning"
author: "Margaret Bassney"
date: "2/24/2022"
output: html_document
---


This basically just has all that Carlotta did just in a markdown file and with housework_satisfied included and na's converted to zero's. We can do something different with them later but i just did that for now. 

```{r}
# import libraries
library(tidyverse)
library(psych)
```

```{r}
# import dataset
dat <- read.csv("TeleCom_Dyad_premeasures.csv")
head(dat)
```
age ethnicity household income relationship length working from home (working from home), heterosexual income race, interracial 

variable names 
birthday, sexualor, race, relation_length, indinc, wfh 

```{r}
# selecting the variables we need
dat <- dat %>%
  select(dyadID, partnum, gender, religion, birthday, sexualor, race, RecordedDate, relation_length, indinc, wfh, starts_with("housework_"), starts_with("grbs_"))
head(dat)
```

```{r}
dat %>%
  select(RecordedDate, relation_length) %>%
  mutate(endRelDate = sub(" .*", "", RecordedDate)) %>%
  rename(startRelDate = relation_length) #%>%
  #mutate(duration = difftime(endRelDate, startRelDate))


#duration = difftime(dat$endRelDate, dat$startRelDate)
#duration = data.frame(dat$endRelDate, dat$startRelDate)
#dat$date_diff  <- as.Date(as.character(dat$endRelDate)) - as.Date(as.character(dat$startRelDate))
#dat$date_diff <- as.data.frame(dat$endRelDate - dat$startRelDate)
```


Renaming/recoding/cleaning 
```{r}
#selecting heterosexual couples only
dat<-filter(dat, sexualor=="Heterosexual")

#calculate relationship length


#Recode Gender Man=0, Woman=1
dat$gender<-recode(dat$gender, "Male"=0, "Woman"=1)

#Recode Work From Home Yes=0, No=1
dat$wfh<-recode(dat$wfh, "Yes"=0, "No"=1)

#rename birthday > age 

#make partnum shorter > just 1 or 2 

```

```{r}
# re-coding housework to be numbers 
dat$housework_1<-recode(dat$housework_1, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_2<-recode(dat$housework_2, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_3<-recode(dat$housework_3, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_4<-recode(dat$housework_4, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_5<-recode(dat$housework_5, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_6<-recode(dat$housework_6, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_7<-recode(dat$housework_7, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_8<-recode(dat$housework_8, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_9<-recode(dat$housework_9, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_10<-recode(dat$housework_10, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_11<-recode(dat$housework_11, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_12<-recode(dat$housework_12, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_13<-recode(dat$housework_13, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
dat$housework_14<-recode(dat$housework_14, "Mostly or always my partner(0-20% me)"=20, 
                        "More likely my partner(20-40% me)"=40, "Shared about equally(40-60% me)"=60, 
                        "More likely me(60-80% me)"=80, "Mostly or always me(80-100% me)"=100)
```

```{r}
# re-coding housework fairness
dat$housework_fair<-recode(dat$housework_fair, "Fair to both you and your partner"=3, "Slightly unfair to you"=4, 
                           "Very fair to me"=1, "Pretty much fair to me"=2, "Very unfair to you"=5)

```

```{r}
# re-coding gender role beliefs 
dat$grbs_1<-recode(dat$grbs_1, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_2<-recode(dat$grbs_2, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_3<-recode(dat$grbs_3, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_4<-recode(dat$grbs_4, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_5<-recode(dat$grbs_5, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_6<-recode(dat$grbs_6, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_7<-recode(dat$grbs_7, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_8<-recode(dat$grbs_8, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_9<-recode(dat$grbs_9, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_10<-recode(dat$grbs_10, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_11<-recode(dat$grbs_11, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_12<-recode(dat$grbs_12, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_13<-recode(dat$grbs_13, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_14<-recode(dat$grbs_14, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_15<-recode(dat$grbs_15, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_16<-recode(dat$grbs_16, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_17<-recode(dat$grbs_17, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_18<-recode(dat$grbs_18, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_19<-recode(dat$grbs_19, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
dat$grbs_20<-recode(dat$grbs_20, "Strongly disagree"=1, "Somewhat disagree"=2, "Neither agree nor disagree"=3, 
                   "Somewhat agree"=4, "Strongly agree"=5)
```

```{r}
# re-coding housework_satisfied
dat$housework_satisfied<-recode(dat$housework_satisfied, "Very dissatisfied" = 1, "Somewhat dissatisfied" = 2, "Neither satisfied nor dissatisfied" = 3, "Somewhat satisfied" = 4, "Very satisfied" = 5)
```


na.rm=false 

```{r}
# re-coding the NA's to be 0's
#dat[is.na(dat)]<- 0
#head(dat)
```


```{r}
# Correlation housework
corr.test(select(dat, housework_1, housework_2, housework_3, housework_4, 
                 housework_5, housework_6, housework_7, housework_8, housework_9, 
                 housework_10, housework_11, housework_12, housework_13, housework_14))$r
```
We can see that there are negative correlations. > type of chore= male/female 

5=Take out garbage, recycling
6=Outdoor work (yard work, rake, mow, shovel snow, garden)  
10=Upkeep of car including repairs, washing and vacuuming  
11=Small repairs around the house


```{r}
# Correlation divided by housework type (typically female vs. typically male)
corr.test(select(dat, housework_1, housework_2, housework_3, housework_4, 
                 housework_7, housework_8, housework_9, 
                 housework_12, housework_13, housework_14))$r

corr.test(select(dat, housework_5, housework_6, 
                 housework_10, housework_11))$r
```

```{r}
# Average of each housework_type
dat %>%
  mutate(avg_housework_female = rowMeans(select(dat, housework_1, housework_2, housework_3, housework_4, housework_7, housework_8, 
         housework_9, housework_12, housework_13, housework_14),na.rm = TRUE))

```

```{r}
# Correlation grbs
dat
corr.test(select(dat, grbs_1, grbs_2,grbs_3,grbs_4,grbs_5,grbs_6,grbs_7,grbs_8,
                 grbs_9, grbs_10, grbs_11, grbs_12, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17, grbs_18, grbs_19, grbs_20))$r
```
We should check for reversed items!! 2y 3y 7 10 12 17


# Reverse score GRBS

# reverse score anything
max + min for a scale and subtract the original score from that.

```{r}
dat_reverse <- dat %>% mutate(grbs_2.r = (1 + 5) - grbs_2,
                              grbs_3.r = (1 + 5) - grbs_3,
                              grbs_7.r = (1 + 5) - grbs_7,
                              grbs_10.r = (1 + 5) - grbs_10,
                              grbs_12.r = (1 + 5) - grbs_12,
                              grbs_17.r = (1 + 5) - grbs_17)
```


```{r}
# Correlation grbs
dat_reverse
corr.test(select(dat_reverse, grbs_1, grbs_2.r,grbs_3.r,grbs_4,grbs_5,grbs_6,grbs_7.r,grbs_8,
                 grbs_9, grbs_10.r, grbs_11, grbs_12.r, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17.r, grbs_18, grbs_19, grbs_20))$r
```


