---
title             : "Satisfying housework division? Gender role beliefs and religion as moderators of housework division and satisfaction"
shorttitle        : "gender roles, housework and satisfaction"

author: 
  - name          : "Carlotta Reinhardt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding 
  - name          : "Margaret Bassney"
    affiliation   : "1"
  - name          : "Anushree Goswami"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Smith College"
   
# authornote: 

bibliography      : ["r-references.bib", "2articles.bib"]


floatsintext      : no
figurelist        : no
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(dplyr)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, include = FALSE}
dat_reverse <- read.csv("dat_reverse.csv")
dat_predyad <- read.csv("predyaddata.csv")
dat_dyad <- read.csv("dyadic.csv")
dat <- read.csv("TeleCom_Dyad_premeasures.csv")
```

# Method
## Participants 
```{r, include = FALSE}
#dataset complete and cleaned
head(dat)
n2 <- count(dat)
n2

n <-length(which(dat_reverse$gender==0))
n
n_indiv <- n*2
n_indiv
```

```{r, include = FALSE}
#create women and men dataset 
dat_reverse_w <- subset(dat_reverse, gender==0)
dat_reverse_m <- subset(dat_reverse, gender==1)

#age 
mean(dat_reverse$age)
meanage<-tapply(dat_reverse$age, dat_reverse$gender, mean)
womenmean <- meanage[2]
menmean <- meanage[1]

sdage<-tapply(dat_reverse$age, dat_reverse$gender, sd)
womensd <- sdage[2]
mensd <- sdage[1]

womenrange <- range(dat_reverse_w$age)
womenrangelow <- womenrange[1]
womenrangelow
womenrangehigh <- womenrange[2]
womenrangehigh

menrange <- range(dat_reverse_m$age)
menrangelow <- menrange[1]
menrangelow
menrangehigh <- menrange[2]
menrangehigh
```

```{r relationship_lengt, include = FALSE}
#relationship length
lengthmean <- round(mean(dat_reverse$relation_yrs, na.rm = TRUE),2)
lengthsd <- round(sd(dat_reverse$relation_yrs, na.rm = TRUE),2)
lengthrange <- range(dat_reverse$relation_yrs, na.rm = TRUE)
lengthrangelow <- round(lengthrange[1],2)
lengthrangehigh <- round(lengthrange[2],2)
``` 

```{r income, include = FALSE}
#income
meninc <- range(dat_reverse_m$indinc, na.rm=TRUE)
meninclow <- meninc[1]
meninclow
meninchigh <- meninc[2]
meninchigh

menincmean <- round(mean(dat_reverse_m$indinc, na.rm=TRUE))

menincsd <- round(sd(dat_reverse_m$indinc, na.rm=TRUE))


womeninc <- range(dat_reverse_w$indinc, na.rm=TRUE)
womeninclow <- womeninc[1]
womeninclow
womeninchigh <- womeninc[2]
womeninchigh

womenincmean <- round(mean(dat_reverse_w$indinc, na.rm=TRUE))

womenincsd <- round(sd(dat_reverse_w$indinc, na.rm=TRUE))
```

```{r, include = FALSE}
#work from home 
dat_reverse_m$wfh
Mwfhyes <- subset(dat_reverse_m, wfh==1)
Mwfhyes <-count(Mwfhyes)
Mwfhno <- subset(dat_reverse_m, wfh==0)
Mwfhno <- count(Mwfhno)
ntotal <- count(dat_reverse_m)
MwfhNA <- ntotal - (Mwfhyes + Mwfhno)
Mperchome <-round((Mwfhyes/ntotal),3)*100
Mpercnohome <-round((Mwfhno/ntotal),3)*100
MpercnohomeNA <-round((MwfhNA/ntotal),3)*100

Wwfhyes <- subset(dat_reverse_w, wfh==1)
Wwfhyes <-count(Wwfhyes)
Wwfhno <- subset(dat_reverse_w, wfh==0)
Wwfhno <- count(Wwfhno)
Wntotal <- count(dat_reverse_m)
WwfhNA <- Wntotal - (Wwfhno + Wwfhyes)
Wperchome <-round((Wwfhyes/Wntotal),3)*100
Wpercnohome <-round((Wwfhno/Wntotal),3)*100
WpercnohomeNA <-round((WwfhNA/Wntotal),3)*100
```

```{r, include = FALSE}
#religion
dat_reverse
Christian <-length(which(dat_reverse$religion=="Christianity"))
Christian <-round((Christian/n_indiv), 2)*100
Athiest <-length(which(dat_reverse$religion=="Athiest"))
Athiest <-round((Athiest/n_indiv), 2)*100
Agnostic <-length(which(dat_reverse$religion=="Agnostic"))
Agnostic<-round((Agnostic/n_indiv), 2)*100
Judaism <-length(which(dat_reverse$religion=="Judaism"))
Judaism<-round((Judaism/n_indiv), 2)*100
Hinduism <-length(which(dat_reverse$religion=="Hinduism"))
Hinduism<-round((Hinduism/n_indiv),2)*100
Islam <-length(which(dat_reverse$religion=="Islam"))
Islam<-round((Hinduism/n_indiv), 2)*100

#other
Other <-length(which(dat_reverse$religion=="Other"))
Other
Agnostic_Other <-length(which(dat_reverse$religion=="Agnostic,Other"))
Agnostic_Other
Christianity_Agnostic <-length(which(dat_reverse$religion=="Agnostic,Other"))
Christianity_Agnostic
Christianity_Athiest <-length(which(dat_reverse$religion=="Christianity,Athiest"))
Christianity_Athiest
other_comb <- Agnostic_Other+Christianity_Agnostic+Christianity_Athiest+Other
other_comb<-round((other_comb/n_indiv), 2)*100

noanswer <-length(which(dat_reverse$religion=="Prefer not to answer"))
noanswer<-round((noanswer/n_indiv), 2)*100

noanswer <-length(which(dat_reverse$religion=="Prefer not to answer"))
noanswer<-round((noanswer/n_indiv), 2)*100


count(dat_reverse, 'religion')
(cTab <- table(dat_reverse$gender, dat_reverse$religion))

tapply(dat_reverse$relation_yrs, dat_reverse$gender, summary)
```


```{r white, include = FALSE}
white <-count(subset(dat_reverse, race=="White or European American"))
```

```{r hisp, include = FALSE}
hisp <-count(subset(dat_reverse, race=="Latinx or Hispanic"))
```

```{r white_hisp, include = FALSE}
white_hisp <-count(subset(dat_reverse, race=="White or European American,Latinx or Hispanic"))
```

```{r asian, include = FALSE}
asian <-count(subset(dat_reverse, race=="Asian or Asian American"))
```

```{r black, include = FALSE}
black <-count(subset(dat_reverse, race=="Black or African American"))
```

```{r mid_east, include = FALSE}
mid_east <-count(subset(dat_reverse, race=="Middle Eastern"))
```

```{r otherCount, include = FALSE}
other <-count(subset(dat_reverse, race=="Other"))
```

```{r naCount, include = FALSE}
na <-count(subset(dat_reverse, race=="Prefer not to answer"))
```

```{r, include = FALSE}
head(subset(dat_reverse, select = 'race'))
count(dat_reverse, 'race')
```

```{r, include = FALSE}
tapply(dat$indinc, dat$gender, summary)
tapply(dat$wfh, dat$gender, summary)
summary(dat_reverse$gender)
tapply(dat_reverse$avg_housework_female, dat_reverse$gender, summary)
tapply(dat_reverse$avg_housework_male, dat_reverse$gender, summary)
tapply(dat_reverse$avg_grbs, dat_reverse$gender, summary)
tapply(dat_reverse$housework_fair, dat_reverse$gender, summary)
tapply(dat_reverse$housework_satisfied, dat_reverse$gender, summary)

table(dat_reverse$race)

tapply(dat_reverse$indinc, dat_reverse$gender, summary)
tapply(dat_reverse$wfh, dat_reverse$gender, summary)

summary(dat_predyad$gender)
tapply(dat_predyad$avg_housework_female, dat_predyad$gender, summary)
tapply(dat_predyad$avg_housework_male, dat_predyad$gender, summary)
tapply(dat_predyad$avg_grbs, dat_predyad$gender, summary)
tapply(dat_predyad$housework_fair, dat_predyad$gender, summary)
tapply(dat_predyad$housework_satisfied, dat_predyad$gender, summary)
```
Originally, `r n2` individuals in a partnership living in the United States of America participated in the study. In our analysis, we excluded all non-heterosexual couples and participants that did not have any partner variables available. In the end, N = `r n` couples (N = `r n_indiv` individuals) have been included in the analysis. Women and men from the final sample of `r n`  adult couples were `r womenmean` (SD = `r womensd`, range = `r womenrangelow`-`r womenrangehigh`) and `r menmean` (SD = `r mensd`, range = `r menrangelow`-`r menrangehigh`) years old, respectively.

The relationships, at the time of the study, have been between `r lengthrangelow` and `r lengthrangehigh` years long, with an average of `r lengthmean` years (SD = `r lengthsd`). The average yearly income was `r menincmean` USD (SD = `r menincsd` USD) for men and `r womenincmean` USD (SD = `r womenincsd` USD) for women. `r Wperchome` % of the women and `r Mperchome` % of the men worked from home, `r Wpercnohome` % of the women and `r Mpercnohome` % of the men did not work from home. No answer to this question was given by the remaining participants (`r MpercnohomeNA` % of the men and `r WpercnohomeNA` % of the women). 

We further looked at men and women based on their religion and race.`r Christian` is the % of the sample that identified as Christian, `r Athiest` % as Athiest, `r Agnostic` % as Agnostic, `r Judaism` % as Jewish, `r Hinduism` % as Hindu and `r Islam` % as Muslim. `r other_comb` % identified had a religious orientation apart from the mentioned ones and `r noanswer` % preferred not to answer this question. `r white` is the % of the sample that were White, `r hisp_white` % that were Hispanic and White, `r black` % that were Black, `r asian` % that were Asian, `r hisp` % that were Hispanic and `r mid_east` % that were Middle Eastern.`r otherCount` % of participants that were another race and `r naCount` % of participants who did not answer the question.

 
## Procedure and Measures
Participating couples for this study were recruited online. The study was conducted in 2020 by Randi Garcia and contained two parts: The first part included a batterie of questionnaires that included all variables used in this study. In a second part, both partners were asked to fill out a daily survey for two weeks.  Participants were instructed to not share their responses with their partner. Participants were compensated for the study if both, they and their partner, completed the questionnaires. For the second part, the daily measures, each participant received $2 per day. All participants gave their informed consent to participate in this study.
In this analysis, selected data from the first batterie of questionnaires were used. The measures of interest are introduced below. 
A multivariate analysis of variances (MANOVA) has been conducted. T-tests were used to assess gender differences in relevant outcome variables.
The analysis was conducted in R [@R-base] and written with the R papaja package [@R-papaja].

```{r include = FALSE}

calc_alpha_ft <- psych::alpha(select(dat_reverse,housework_1, housework_2, housework_3, housework_4, housework_7, housework_8, housework_9,housework_12, housework_13, housework_14))
female_tasks_alpha<-calc_alpha_ft$raw_alpha
```

```{r, include = FALSE}

calc_alpha_mt<- psych::alpha(select(dat_reverse,housework_5, housework_6,  housework_10, housework_11))
male_tasks_alpha<-calc_alpha_mt$total$raw_alpha
```

```{r, include = FALSE}
calc_grb_alpha<- psych::alpha(select(dat_reverse, grbs_1, grbs_2.r,grbs_3.r,grbs_4,grbs_5,grbs_6,grbs_7.r,grbs_8,
                 grbs_9, grbs_10.r, grbs_11, grbs_12.r, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17.r, grbs_18, grbs_19, grbs_20))

grb_alpha<-calc_grb_alpha$total$raw_alpha
```

### Demographic Variables 
Participants were asked to report several demographic data. We were interested in the participants gender, the couples' relationship length, the yearly income of each partner, their work from home status, religion affiliation, and race. 

### Housework Distribution  
The scale *Who does what?*, developed by @cowan_when_1992, measures the percentages of who performs which chores and household activities through 14 statements that participants have to rate on a five point Likert Scale according to how often they do the chore mentioned in the statement (1 = *0 - 20 %* to 5 = *80 - 100 %*). Example questions include "make beds or change bed linens" and "take out garbage, recycling". Based on prior research and correlation analyses, we decided to split this scale into typically male and typically female tasks. The scale was reliable with a Cronbachs Alpha of `r female_tasks_alpha` for female tasks and `r male_tasks_alpha` for male tasks.

### Gender Role Beliefs 
Gender Role Beliefs are quantified through the *Gender Role Belief Scale* (GRBS) developed by @kerr_development_1996-1. This self report scale measures gender ideology and beliefs about appropriate behavior for men and women. Example ideologies include "women should not expect men to offer them seats on buses" and "the husband should be regarded as the legal representative of the family in all matters of law". Participants rated how much they agreed on these sentences on a 5 point Likert Scale (1 = *Strongly Disagree* to 5 = *Strongly Agree*). The scale showed a high reliability with a Cronbachs Alpha of `r grb_alpha`.

### Housework Satisfaction
Within the questionnaire, the question "How satisfied are you with the division of household tasks?" was included to quantify the satisfaction with the division of housework tasks between the two partners. Participants responded on a 5 point Likert scale (1 = "very dissatisfied" to 5 = "very satisfied"). 


# Results

## Preliminary Analysis 
Results of the preliminary analysis are shown in Table 1. T-tests showed that men are doing significantly more male housework tasks than women while women perform significantly more typically female tasks around the house. Satisfaction with the distribution of housework did not differ significantly between male and female partners.

```{r, include = FALSE}
hwf_t_test<-t.test(dat_reverse_m$avg_housework_female, dat_reverse_w$avg_housework_female, paired = TRUE, alternative = "two.sided")
```

```{r, include = FALSE}
hwm_t_test<-t.test(dat_reverse_m$avg_housework_male, dat_reverse_w$avg_housework_male, paired = TRUE, alternative = "two.sided")
```

```{r, include = FALSE}
sat_t_test<-t.test(dat_reverse_m$housework_satisfied, dat_reverse_w$housework_satisfied, paired = TRUE, alternative = "two.sided")
```

```{r, include = FALSE}
#t.test(dat_reverse$avg_grbs, dat_reverse$gender, paired = T, alternative = "two.sided")
#this was wrong
```

```{r, include = FALSE}
grbs_t_test<-t.test(dat_reverse_m$avg_grbs, dat_reverse_w$avg_grbs, paired = T, alternative = "two.sided")
```

```{r, include=FALSE}
 attach(dat_reverse)
         pairwise.t.test(avg_grbs, gender, p.adjust.method="bonferroni", paired=T)
```

```{r, include = FALSE}
fair_t_test<-t.test(dat_reverse$housework_fair, dat_reverse$relation_yrs, paired = TRUE, alternative = "two.sided")
```

```{r, include = FALSE}
age_t_test<-t.test(dat_reverse_m$age,dat_reverse_w$age, paired = TRUE, alternative = "two.sided")
```

```{r}
p_vals<-rbind(hwm_t_test$p.value,hwf_t_test$p.value,grbs_t_test$p.value,sat_t_test$p.value,fair_t_test$p.value)
```

```{r}
t_stat<-rbind(hwm_t_test$statistic,hwf_t_test$statistic,grbs_t_test$statistic,sat_t_test$statistic,fair_t_test$statistic)
```

```{r}
p_stat_vals<-cbind(t_stat,p_vals)
```

```{r}
p_stat_vals<-as.data.frame(p_stat_vals)
p_stat_vals<-p_stat_vals%>%
  mutate(T_Statistic = t,
         P_value = V2)%>%
  select(T_Statistic,P_value)
```

```{r}
rownames(p_stat_vals) <- c("Typically Male Housework","Typically Female Housework","Gender Role Beleifs","Satisfaction with Distrubution of Housework","Perceived Housework Fairness")
```


\newpage
```{r}
descriptive_stats <- dat_reverse %>% group_by(gender) %>%
  mutate(gender = ifelse(gender == 0, "Male","Female"))%>%
  summarize(
    Mean = mean(avg_housework_female,na.rm = TRUE)
    , Median = median(avg_housework_female,na.rm = TRUE)
    , SD = sd(avg_housework_female,na.rm = TRUE)
    , Min = min(avg_housework_female,na.rm = TRUE)
    , Max = max(avg_housework_female,na.rm = TRUE))
descriptive_stats[, -1] <- printnum(descriptive_stats[, -1])
apa_table(
  descriptive_stats
  , caption = "Descriptive statistics of typically female tasks by Gender"
  , note = "This table was created with apa_table()."
  , escape = TRUE)
```

```{r, include=FALSE}
#descriptive_stats <- dat_reverse %>% group_by(gender) %>%
#  summarize(
#    Mean = mean(avg_housework_female)
#    , Median = median(avg_housework_female)
#    , SD = sd(avg_housework_female)
#    , Min = min(avg_housework_female)
#    , Max = max(avg_housework_female))
#descriptive_stats[, -1] <- printnum(descriptive_stats[, -1])
#apa_table(
#  descriptive_stats
#  , caption = "Descriptive statistics of typically female tasks by Gender"
#  , note = "This table was created with apa_table()."
#  , escape = TRUE)

```



```{r}
GenderDifferences <- dat_predyad%>%group_by(gender) %>%
  mutate(mean_housework_male = mean(avg_housework_male, na.rm = TRUE),
         mean_housework_female = mean(avg_housework_female, na.rm = TRUE),
         mean_grbs = mean(avg_grbs),
         gender = ifelse(gender == 0, "Male","Female"),
         meanSatisfaction = mean(housework_satisfied),
         meanFairness = mean(housework_fair,na.rm = TRUE))%>%
  select(mean_housework_male,mean_housework_female,mean_grbs,meanSatisfaction,meanFairness)

```

```{r}
## transpose means 
GenderDifferences<-t(GenderDifferences)
```

```{r}
GenderDifferences<-as.data.frame(GenderDifferences)
```




```{r}
## select rows i want
GenderDifferences<-GenderDifferences%>%
  select(c(1,2))
```

```{r}
GenderDifferences<-GenderDifferences[-1,]
```


```{r}
GenderDifferences<-cbind(GenderDifferences,p_stat_vals)
```


```{r}
GenderDifferences <- GenderDifferences %>%
  rename("Female Means" = V1,"Male Means" = V2, "T Statistic" = T_Statistic,"P Value" = P_value)
```

```{r}
rownames(GenderDifferences) <- c("Typically Male Housework","Typically Female Housework","Gender Role Beleifs","Satisfaction with Distrubution of Housework","Perceived Housework Fairness")
```

```{r}
apa_table(
  GenderDifferences
  , caption = "Gender Differences"
  , note = "This table was created with apa_table()."
  , escape = TRUE)
```


# References

::: {#refs custom-style="Bibliography"}
:::
