---
title             : "Method Section: Measures and Descriptive Statistics Write-up"
shorttitle        : "housework analysis"

author: 
  - name          : "Carlotta Reinhardt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       :
    email         :
    role:

  - name          : "Margaret Bassney"
    affiliation   : "1,2"
    role:
      
  - name          : "Anushree Goswami"
    affiliation   : "1,2,3"
    role:    


affiliation:
  - id            : "1"
    institution   : "Smith College"
  - id            : "2"
    institution   : "Smith College"
  - id            : "3"
    institution   : "Smith College"

   

authornote: 

abstract: 
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]


floatsintext      : no
figurelist        : no
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Method
## Participants 
Originally, `n2` individuals in a partnership living in the United States of America participated in the study. In our analysis, we excluded all non-heterosexual couples and participants that did not have any partner variables available. In the end, N=`n` couples have been included in the analysis. Men and women from the final sample of `n`  adult couples were `womenmean` (SD = `womensd`, range = `womenrange`) and `menmean` (SD = `mensd`, range = `menrange`) years old, respectively. 
The relationship were between `lengthrangelow` and `lengthrangehigh` years long, with an average of `lengthrange` years (SD = `lengthsd`). 


Income 

Work from home 

racial groups 

## Measures

Variables:
**partnum** Indicates Partner number 1





- Scale used to measure each variable you intend to use
- Give the original variable name from the original data set 

Variables:
**Partner number** (partnum) - 1 or 2
**Gender** (gender) - 0 or 1
**Religion** - text

```{r, include = FALSE}
dat_reverse <- read.csv("dat_reverse.csv")
dat_predyad <- read.csv("predyaddata.csv")
dat_dyad <- read.csv("dyadic.csv")
dat <- read.csv("TeleCom_Dyad_premeasures.csv")
```


```{r include = FALSE}
a <- psych::alpha(select(dat_reverse,housework_1, housework_2, housework_3, housework_4, housework_7, housework_8, housework_9,housework_12, housework_13, housework_14))
d<-a$raw_alpha
```


```{r, include = FALSE}
<<<<<<< HEAD
#b <- alpha(select(dat,housework_5, housework_6, 
#                 housework_10, housework_11))
#c<-b$total$raw_alpha
=======
b <- psych::alpha(select(dat_reverse,housework_5, housework_6, 

                housework_10, housework_11))
c<-b$total$raw_alpha
>>>>>>> fec415a6fe60b3c2770f2b349da67f955357d1cd
```



```{r, include = FALSE}
e <- psych::alpha(select(dat_reverse, grbs_1, grbs_2.r,grbs_3.r,grbs_4,grbs_5,grbs_6,grbs_7.r,grbs_8,
                 grbs_9, grbs_10.r, grbs_11, grbs_12.r, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17.r, grbs_18, grbs_19, grbs_20))
f<-e$total$raw_alpha
```

**gender** Describes which gender the individual identifies with. Examples include "woman", "man", and "transgender".

**religion** Describes the religion that the individual associates with the most. Examples include "Christianity", "Islam", and "Atheist".

**who does what?** developed by Cowan and Cowan in 1992. This scale measures the percentages of who performs which chores and household activities with 14 questions. Example items include " "Make beds or change bed linens"  and "Take out garbage, recycling" measured on a 1-*0-20%* to 5-*80-100%* scale. We split this scale into typically male and typically female tasks. The scale was reliable with a chronbachs alpha of `r d` for female tasks and `r c` for male tasks.
Average Housework male - 0 to 100
Average housework female - 0 to 100

**grbs** Quantifies the gender role beliefs through the Gender Role Belief Scale (GRBS) which was developed by Paula S. Kerr and Ronald R.Holden (1996). This self report scale measures gender ideology and beliefs about appropriate behavior for men and women. Example Items include "Women should not expect men to offer them seats on busses" and "The husband should be regarded as the legal representative of the family in all matters of law" measured on a 1-*Strongly Disagree* to 5-*Strongly Agree* scale.

**who does what?** developed by Cowan and Cowan in 1992. This scale measures the percentages of who performs which chores and household activities with 14 questions. Example items include "Make beds or change bed linens" and "Take out garbage, recycling" measured on a 1-*0-20%* to 5-*80-100%* scale. We split this scale into typically male and typically female tasks. The scale was reliable with a chronbachs alpha of `r d` for female tasks and `r c` for male tasks.
Average Housework male - 0 to 100
Average housework female - 0 to 100

**relation_length** The date when both people first got together in mm/dd/yyyy which signifies the start of their relationship.

**relationship length** Measures the length of the couples' relationship in years. We calculated this value by subtracting the relation_length from the date the survey was filled out.

**Gender Role Beliefs**Gender Role Belief Scale (GRBS) developed by Paula S. Kerr and Ronald R.Holden(1996). This self report scale measures gender ideology and beliefs about appropriate behavior for men and women. Example Items include "Women should not expect men to offer them seats on busses" and "The husband should be regarded as the legal representative of the family in all matters of law" measured on a 1-*Strongly Disagree* to 5-*Strongly Agree* scale. The scale was reliable with a chronbachs alpha of `r f`. 

**housework_fair** Quantifies the fairness of the division of housework tasks between the two partners, on a scale of 1 to 5. A fairness score of 1 means "very unfair to you", 2 means "slightly unfair to you", 3 means "fair to both you and your partner", 4 means "pretty much fair to me" and 5 means "very fair to me". 

**housework_satisfied** Quantifies the satisfaction of the division of housework tasks between the two partners, on a scale of 1 to 5. A satisfaction score of 1 means "very dissatisfied", 2 means "somewhat dissatisfied", 3 means "neither satisfied not dissatisfied", 4 means "somewhat satisfied" and 5 means "very satisfied".


**partnum2** Indicates Partner number 2










In our analysis, we excluded all non-heterosexual couples and participants that did not have any partner variables available. In the end, N= couples will be included in the analysis  





In our analysis, we excluded all non-heterosexual couples and participants that did not have any partner variables available. In the end, N=`n` couples have been included in the analysis. 


age, gender, relationship length, wfh

######Average GRBS - 0 to 100

<<<<<<< HEAD
=======


>>>>>>> fec415a6fe60b3c2770f2b349da67f955357d1cd

# Results
## Participant Demographics

```{r}
#dataset complete and cleaned
head(dat)
n2 <- count(dat)
n2

n <- count(dat_reverse)/2
n
```

```{r}
#create women and men dataset 
dat_reverse_w <- subset(dat_reverse, gender==0)
dat_reverse_m <- subset(dat_reverse, gender==1)

#age 
mean(dat_reverse$age)
meanage<-tapply(dat_reverse$age, dat_reverse$gender, mean)
womenmean <- meanage[2]
menmean <- meanage[1]

sdage<-tapply(dat_reverse$age, dat_reverse$gender, sd)
womensd <- sdage[2]
mensd <- sdage[1]

<<<<<<< HEAD
womenrange <- range(dat_reverse_w$age)
womenrangelow <- womenrange[1]
womenrangelow
womenrangehigh <- womenrange[2]
womenrangehigh

menrange <- range(dat_reverse_m$age)
menrangelow <- menrange[1]
menrangelow
menrangehigh <- menrange[2]
menrangehigh
```
Originally, `n2` individuals in a partnership living in the United States of America participated in the study. In our analysis, we excluded all non-heterosexual couples and participants that did not have any partner variables available. In the end, N=`n` couples have been included in the analysis. Men and women from the final sample of `n`  adult couples were `womenmean` (SD = `womensd`, range = `womenrangelow`-`womenrangehigh`) and `menmean` (SD = `mensd`, range = `menrangelow`-`menrangehigh`) years old, respectively. 
The relationship were between `lengthrangelow` and `lengthrangehigh` years long, with an average of `lengthrange` years (SD = `lengthsd`). The average income was `menincmean` USD (SD = `menincsd`) for men and `womenincmean` USD (SD = `womenincsd`) for women.   
=======
rangeage <-tapply(dat_reverse$age, dat_reverse$gender, range)

womenrange <- rangeage[2]
menrange <- rangeage[1]

womenrange
menrange
#how do I show them individually?
>>>>>>> fec415a6fe60b3c2770f2b349da67f955357d1cd



<<<<<<< HEAD
```{r}
#relationship length
lengthmean <- round(mean(dat_reverse$relation_yrs, na.rm = TRUE),2)
lengthsd <- round(sd(dat_reverse$relation_yrs, na.rm = TRUE),2)
lengthrange <- range(dat_reverse$relation_yrs, na.rm = TRUE)
lengthrangelow <- round(lengthrange[1],2)
lengthrangehigh <- round(lengthrange[2],2)
``` 

```{r}
#income
meninc <- range(dat_reverse_m$indinc, na.rm=TRUE)
meninclow <- meninc[1]
meninclow
meninchigh <- meninc[2]
meninchigh

menincmean <- mean(dat_reverse_m$indinc, na.rm=TRUE)

menincsd <- sd(dat_reverse_m$indinc, na.rm=TRUE)


womeninc <- range(dat_reverse_w$indinc, na.rm=TRUE)
womeninclow <- womeninc[1]
womeninclow
womeninchigh <- womeninc[2]
womeninchigh

womenincmean <- mean(dat_reverse_w$indinc, na.rm=TRUE)

womenincsd <- sd(dat_reverse_w$indinc, na.rm=TRUE)
```

```{r}
#work from home 
dat_reverse_m$wfh
Mwfhyes <- subset(dat_reverse_m, wfh==1)
Mwfhyes <-count(Mwfhyes)
Mwfhno <- subset(dat_reverse_m, wfh==0)
Mwfhno <- count(Mwfhno)
ntotal <- count(dat_reverse_m)
MwfhNA <- ntotal - (Mwfhyes + Mwfhno)
Mpercnohome <-round((Mwfhno/ntotal),2)

Wwfhyes <- subset(dat_reverse_w, wfh==1)
Wwfhyes <-count(Wwfhyes)
Wwfhno <- subset(dat_reverse_w, wfh==0)
Wwfhno <- count(Wwfhno)
Wntotal <- count(dat_reverse_m)
WwfhNA <- Wntotal - (Wwfhno + Wwfhyes)
```

```{r}
#religion
dat_reverse
Christian <-count(subset(dat_reverse, religion=="Christianity"))
Christian
Athiest <-count(subset(dat_reverse, religion=="Athiest"))
Athiest
Agnostic <-count(subset(dat_reverse, religion=="Agnostic"))
Agnostic
Judaism <-count(subset(dat_reverse, religion=="Judaism"))
Judaism
Hinduism <-count(subset(dat_reverse, religion=="Hinduism"))
Hinduism
Islam <-count(subset(dat_reverse, religion=="Islam"))
Islam
Other <-count(subset(dat_reverse, religion=="Other"))
Other
Agnostic_Other <-count(subset(dat_reverse, religion=="Agnostic,Other"))
Agnostic_Other
Christianity_Agnostic <-count(subset(dat_reverse, religion=="Agnostic,Other"))
Christianity_Agnostic
Christianity_Athiest <-count(subset(dat_reverse, religion=="Christianity,Athiest"))
Christianity_Athiest
noanswer <-count(subset(dat_reverse, religion=="Prefer not to answer"))
noanswer
=======
tapply(dat_reverse$age, dat_reverse$gender, summary)
summary(dat_reverse$sexualor)
# dat_women
# dat_men


>>>>>>> fec415a6fe60b3c2770f2b349da67f955357d1cd

count(dat_reverse, 'religion')
(cTab <- table(dat_reverse$gender, dat_reverse$religion))

tapply(dat_reverse$relation_yrs, dat_reverse$gender, summary)
#weird - relationship length differs in men and women... 
```

<<<<<<< HEAD
```{r}
#race
table(dat$race)

```

```{r}
tapply(dat$indinc, dat$gender, summary)
tapply(dat$wfh, dat$gender, summary)
summary(overall_data$gender)
tapply(overall_data$avg_housework_female, overall_data$gender, summary)
tapply(overall_data$avg_housework_male, overall_data$gender, summary)
tapply(overall_data$avg_grbs, overall_data$gender, summary)
tapply(overall_data$housework_fair, overall_data$gender, summary)
tapply(overall_data$housework_satisfied, overall_data$gender, summary)
=======
table(dat_reverse$race)

tapply(dat_reverse$indinc, dat_reverse$gender, summary)
tapply(dat_reverse$wfh, dat_reverse$gender, summary)

summary(dat_predyad$gender)
tapply(dat_predyad$avg_housework_female, dat_predyad$gender, summary)
tapply(dat_predyad$avg_housework_male, dat_predyad$gender, summary)
tapply(dat_predyad$avg_grbs, dat_predyad$gender, summary)
tapply(dat_predyad$housework_fair, dat_predyad$gender, summary)
tapply(dat_predyad$housework_satisfied, dat_predyad$gender, summary)
>>>>>>> fec415a6fe60b3c2770f2b349da67f955357d1cd
```


Include:
1. sample size (number of individuals and dyads)
2. % of gender
3. % of racial groups
4. income range, work from home?
5. t-tests


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::



```{r, include=FALSE}
descriptive_stats <- dat_reverse %>% group_by(gender) %>%
  summarize(
    Mean = mean(avg_housework_female)
    , Median = median(avg_housework_female)
    , SD = sd(avg_housework_female)
    , Min = min(avg_housework_female)
    , Max = max(avg_housework_female))
descriptive_stats[, -1] <- printnum(descriptive_stats[, -1])
apa_table(
  descriptive_stats
  , caption = "Descriptive statistics of typically female tasks by Gender"
  , note = "This table was created with apa_table()."
  , escape = TRUE)

```



```{r, include=FALSE}
descriptive_stats_t_tests <- as.data.frame(womenmean,menmean)
apa_table(
  descriptive_stats_t_tests
  , caption = "Descriptive statistics of typically female tasks by Gender"
  , note = "This table was created with apa_table()."
  , escape = TRUE)

```





