---
title             : "Method Section: Measures and Descriptive Statistics Write-up"
shorttitle        : "housework analysis"

author: 
  - name          : "Carlotta Reinhardt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding 
  - name          : "Margaret Bassney"
    affiliation   : "1"
  - name          : "Anushree Goswami"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Smith College"
   
# authornote: 

abstract: "hi"
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]


floatsintext      : no
figurelist        : no
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, include = FALSE}
dat_reverse <- read.csv("dat_reverse.csv")
dat_predyad <- read.csv("predyaddata.csv")
dat_dyad <- read.csv("dyadic.csv")
dat <- read.csv("TeleCom_Dyad_premeasures.csv")
```

# Method
## Participants 
```{r, include = FALSE}
#dataset complete and cleaned
head(dat)
n2 <- count(dat)
n2

n <-length(which(dat_reverse$gender==0))
n
n_indiv <- n*2
n_indiv
```



```{r, include = FALSE}
#create women and men dataset 
dat_reverse_w <- subset(dat_reverse, gender==0)
dat_reverse_m <- subset(dat_reverse, gender==1)

#age 
mean(dat_reverse$age)
meanage<-tapply(dat_reverse$age, dat_reverse$gender, mean)
womenmean <- meanage[2]
menmean <- meanage[1]

sdage<-tapply(dat_reverse$age, dat_reverse$gender, sd)
womensd <- sdage[2]
mensd <- sdage[1]


womenrange <- range(dat_reverse_w$age)
womenrangelow <- womenrange[1]
womenrangelow
womenrangehigh <- womenrange[2]
womenrangehigh

menrange <- range(dat_reverse_m$age)
menrangelow <- menrange[1]
menrangelow
menrangehigh <- menrange[2]
menrangehigh
```


```{r, include = FALSE}
#relationship length
lengthmean <- round(mean(dat_reverse$relation_yrs, na.rm = TRUE),2)
lengthsd <- round(sd(dat_reverse$relation_yrs, na.rm = TRUE),2)
lengthrange <- range(dat_reverse$relation_yrs, na.rm = TRUE)
lengthrangelow <- round(lengthrange[1],2)
lengthrangehigh <- round(lengthrange[2],2)
``` 

```{r, include = FALSE}
#income
meninc <- range(dat_reverse_m$indinc, na.rm=TRUE)
meninclow <- meninc[1]
meninclow
meninchigh <- meninc[2]
meninchigh

menincmean <- round(mean(dat_reverse_m$indinc, na.rm=TRUE))

menincsd <- round(sd(dat_reverse_m$indinc, na.rm=TRUE))


womeninc <- range(dat_reverse_w$indinc, na.rm=TRUE)
womeninclow <- womeninc[1]
womeninclow
womeninchigh <- womeninc[2]
womeninchigh

womenincmean <- round(mean(dat_reverse_w$indinc, na.rm=TRUE))

womenincsd <- round(sd(dat_reverse_w$indinc, na.rm=TRUE))
```

```{r, include = FALSE}
#work from home 
dat_reverse_m$wfh
Mwfhyes <- subset(dat_reverse_m, wfh==1)
Mwfhyes <-count(Mwfhyes)
Mwfhno <- subset(dat_reverse_m, wfh==0)
Mwfhno <- count(Mwfhno)
ntotal <- count(dat_reverse_m)
MwfhNA <- ntotal - (Mwfhyes + Mwfhno)
Mperchome <-round((Mwfhyes/ntotal),3)*100
Mpercnohome <-round((Mwfhno/ntotal),3)*100
MpercnohomeNA <-round((MwfhNA/ntotal),3)*100

Wwfhyes <- subset(dat_reverse_w, wfh==1)
Wwfhyes <-count(Wwfhyes)
Wwfhno <- subset(dat_reverse_w, wfh==0)
Wwfhno <- count(Wwfhno)
Wntotal <- count(dat_reverse_m)
WwfhNA <- Wntotal - (Wwfhno + Wwfhyes)
Wperchome <-round((Wwfhyes/Wntotal),3)*100
Wpercnohome <-round((Wwfhno/Wntotal),3)*100
WpercnohomeNA <-round((WwfhNA/Wntotal),3)*100
```

```{r, include = FALSE}
#religion
dat_reverse
Christian <-length(which(dat_reverse$religion=="Christianity"))
Christian <-round((Christian/n_indiv), 2)*100
Athiest <-length(which(dat_reverse$religion=="Athiest"))
Athiest <-round((Athiest/n_indiv), 2)*100
Agnostic <-length(which(dat_reverse$religion=="Agnostic"))
Agnostic<-round((Agnostic/n_indiv), 2)*100
Judaism <-length(which(dat_reverse$religion=="Judaism"))
Judaism<-round((Judaism/n_indiv), 2)*100
Hinduism <-length(which(dat_reverse$religion=="Hinduism"))
Hinduism<-round((Hinduism/n_indiv),2)*100
Islam <-length(which(dat_reverse$religion=="Islam"))
Islam<-round((Hinduism/n_indiv), 2)*100

#other
Other <-length(which(dat_reverse$religion=="Other"))
Other
Agnostic_Other <-length(which(dat_reverse$religion=="Agnostic,Other"))
Agnostic_Other
Christianity_Agnostic <-length(which(dat_reverse$religion=="Agnostic,Other"))
Christianity_Agnostic
Christianity_Athiest <-length(which(dat_reverse$religion=="Christianity,Athiest"))
Christianity_Athiest
other_comb <- Agnostic_Other+Christianity_Agnostic+Christianity_Athiest+Other
other_comb<-round((other_comb/n_indiv), 2)*100


noanswer <-length(which(dat_reverse$religion=="Prefer not to answer"))
noanswer<-round((noanswer/n_indiv), 2)*100


count(dat_reverse, 'religion')
(cTab <- table(dat_reverse$gender, dat_reverse$religion))

tapply(dat_reverse$relation_yrs, dat_reverse$gender, summary)
#weird - relationship length differs in men and women... 
```

```{r, include = FALSE}
#race
white <-count(subset(dat_reverse, race=="White or European American"))
white
hisp <-count(subset(dat_reverse, race=="Latinx or Hispanic"))
hisp
white_hisp <-count(subset(dat_reverse, race=="White or European American,Latinx or Hispanic"))
white_hisp
asian <-count(subset(dat_reverse, race=="Asian or Asian American"))
asian
black <-count(subset(dat_reverse, race=="Black or African American"))
black
mid_east <-count(subset(dat_reverse, race=="Middle Eastern"))
mid_east
other <-count(subset(dat_reverse, race=="Other"))
other
na <-count(subset(dat_reverse, race=="Prefer not to answer"))
na
```

```{r, include = FALSE}
#race
#table(dat$race)

head(subset(dat_reverse, select = 'race'))
count(dat_reverse, 'race')
```

```{r, include = FALSE}
tapply(dat$indinc, dat$gender, summary)
tapply(dat$wfh, dat$gender, summary)
summary(dat_reverse$gender)
tapply(dat_reverse$avg_housework_female, dat_reverse$gender, summary)
tapply(dat_reverse$avg_housework_male, dat_reverse$gender, summary)
tapply(dat_reverse$avg_grbs, dat_reverse$gender, summary)
tapply(dat_reverse$housework_fair, dat_reverse$gender, summary)
tapply(dat_reverse$housework_satisfied, dat_reverse$gender, summary)

table(dat_reverse$race)

tapply(dat_reverse$indinc, dat_reverse$gender, summary)
tapply(dat_reverse$wfh, dat_reverse$gender, summary)

summary(dat_predyad$gender)
tapply(dat_predyad$avg_housework_female, dat_predyad$gender, summary)
tapply(dat_predyad$avg_housework_male, dat_predyad$gender, summary)
tapply(dat_predyad$avg_grbs, dat_predyad$gender, summary)
tapply(dat_predyad$housework_fair, dat_predyad$gender, summary)
tapply(dat_predyad$housework_satisfied, dat_predyad$gender, summary)
```
Originally, `r n2` individuals in a partnership living in the United States of America participated in the study. In our analysis, we excluded all non-heterosexual couples and participants that did not have any partner variables available. In the end, N = `r n` couples (N = `r n_indiv` individuals) have been included in the analysis. Men and women from the final sample of `r n`  adult couples were `r womenmean` (SD = `r womensd`, range = `r womenrangelow`-`r womenrangehigh`) and `r menmean` (SD = `r mensd`, range = `r menrangelow`-`r menrangehigh`) years old, respectively. 

The relationships, at the time of the study, have been between `r lengthrangelow` and `r lengthrangehigh` years long, with an average of `r lengthmean` years (SD = `r lengthsd`). The average yearly income was `r menincmean` USD (SD = `r menincsd` USD) for men and `r womenincmean` USD (SD = `r womenincsd` USD) for women. `r Wperchome` % of the women and `r Mperchome` % of the men worked from home, `r Wpercnohome` % of the women and `r Mpercnohome` % of the men did not work from home. No answer to this question was given by the remaining participants (`r MpercnohomeNA` % of the men and `r WpercnohomeNA` % of the women). 

`r Christian` % of the sample identified as Christian, `r Athiest` % as Athiest, `r Agnostic` % as Agnostic, `r Judaism` % as Jewish, `r Hinduism` % as Hindu and `r Islam` % as Muslim. `r other_comb` % identified had a religious orientation apart from the mentioned ones and `r noanswer` % preferred not to answer this question.

## Procedure and Measures
Couples were recruited online(??) and filled out all questionnaires online. The participants received a description of the procedure before filling out the questionnaires. They were told to fill out the questionnaire by themselves, not with their partners. Participants were not compensated for participating in this study (?).  
This study used data from a larger study that was conducted in 2020 (??). The variables of interest are introduced below. 
A multivariate analysis of variances (MANOVA) has been conducted. T-tests were used to assess gender differences in relevant outcome variables as well as .... 
The analysis was conducted in R [@R-base] and written with the R papaja package [@R-papaja].

```{r include = FALSE}

calc_alpha_ft <- psych::alpha(select(dat_reverse,housework_1, housework_2, housework_3, housework_4, housework_7, housework_8, housework_9,housework_12, housework_13, housework_14))
female_tasks_alpha<-calc_alpha_ft$raw_alpha
```

```{r, include = FALSE}

calc_alpha_mt<- psych::alpha(select(dat_reverse,housework_5, housework_6,  housework_10, housework_11))
male_tasks_alpha<-calc_alpha_mt$total$raw_alpha
```


```{r, include = FALSE}
calc_grb_alpha<- psych::alpha(select(dat_reverse, grbs_1, grbs_2.r,grbs_3.r,grbs_4,grbs_5,grbs_6,grbs_7.r,grbs_8,
                 grbs_9, grbs_10.r, grbs_11, grbs_12.r, grbs_13, grbs_14, grbs_15, 
                 grbs_16, grbs_17.r, grbs_18, grbs_19, grbs_20))

grb_alpha<-calc_grb_alpha$total$raw_alpha
```

### Demographic variables 
Participants were asked about several demographic variables, like gender, relationship length, their income, whether they work from home, their religion as well as race. 

### Housework Distribution  
The scale *Who does what?* was developed by Cowan and Cowan in 1992 (here we need the actual source and cite it). This scale measures the percentages of who performs which chores and household activities with 14 questions. Example items include " "Make beds or change bed linens"  and "Take out garbage, recycling" measured on a five Likert scale (1 = *0-20%* to 5 = *80-100%*). We split this scale into typically male and typically female tasks. The scale was reliable with a Cronbachs Alpha of `r female_tasks_alpha` for female tasks and `r male_tasks_alpha` for male tasks.

### Gender Role Beliefs 
Quantifies the gender role beliefs through the Gender Role Belief Scale (GRBS) which was developed by Paula S. Kerr and Ronald R.Holden (1996). This self report scale measures gender ideology and beliefs about appropriate behavior for men and women. Example Items include "Women should not expect men to offer them seats on busses" and "The husband should be regarded as the legal representative of the family in all matters of law" measured on a 1-*Strongly Disagree* to 5-*Strongly Agree* scale.

Gender Role Belief Scale (GRBS) developed by Paula S. Kerr and Ronald R.Holden(1996). This self report scale measures gender ideology and beliefs about appropriate behavior for men and women. Example Items include "Women should not expect men to offer them seats on busses" and "The husband should be regarded as the legal representative of the family in all matters of law" measured on a 1-*Strongly Disagree* to 5-*Strongly Agree* scale. The scale was reliable with a chronbachs alpha of `r grb_alpha`. 

### Housework Satisfaction
Quantifies the satisfaction of the division of housework tasks between the two partners, on a scale of 1 to 5. A satisfaction score of 1 means "very dissatisfied", 2 means "somewhat dissatisfied", 3 means "neither satisfied not dissatisfied", 4 means "somewhat satisfied" and 5 means "very satisfied".


# Results


## Preliminary Analysis 
Results of the preliminary analysis are shown in Table 1. Age differed significantly between men and women, as did the housework tasks. 

1. Average housework female and average housework male
```{r, include = FALSE}
t.test(dat_reverse_m$avg_housework_female, dat_reverse_w$avg_housework_female, paired = TRUE, alternative = "two.sided")
```

```{r, include = FALSE}
t.test(dat_reverse_m$avg_housework_male, dat_reverse_w$avg_housework_male, paired = TRUE, alternative = "two.sided")
```


2. Housework satisfaction and gender
```{r, include = FALSE}
t.test(dat_reverse_m$housework_satisfied, dat_reverse_w$housework_satisfied, paired = TRUE, alternative = "two.sided")
```

Since the p-value is much smaller than 0.05, we fail to reject the null hypothesis. This means that the true difference in both the means is equal to 0.

3. Gender role beliefs and gender
```{r, include = FALSE}
#t.test(dat_reverse$avg_grbs, dat_reverse$gender, paired = T, alternative = "two.sided")
```

pairwise t test 


```{r, include = FALSE}
t.test(dat_reverse_m$avg_grbs, dat_reverse_w$avg_grbs, paired = T, alternative = "two.sided")
```

Since the p-value is much smaller than 0.05, we reject the null hypothesis. This means that the true difference in both the means is not equal to 0.

4. Housework fairness and relationship length
```{r, include = FALSE}
t.test(dat_reverse$housework_fair,dat_reverse$relation_yrs, paired = TRUE, alternative = "two.sided")
```

```{r, include = FALSE}
t.test(dat_reverse_m$age,dat_reverse_w$age, paired = TRUE, alternative = "two.sided")
```


Since the p-value is much smaller than 0.05, we  reject the null hypothesis. This means that the probability of getting this difference in means,assuming the null hypothesis is true, is very unlikely. 




\newpage
```{r}
descriptive_stats <- dat_reverse %>% group_by(gender) %>%
  mutate(gender = ifelse(gender == 0, "Male","Female"))%>%
  summarize(
    Mean = mean(avg_housework_female,na.rm = TRUE)
    , Median = median(avg_housework_female,na.rm = TRUE)
    , SD = sd(avg_housework_female,na.rm = TRUE)
    , Min = min(avg_housework_female,na.rm = TRUE)
    , Max = max(avg_housework_female,na.rm = TRUE))
descriptive_stats[, -1] <- printnum(descriptive_stats[, -1])
apa_table(
  descriptive_stats
  , caption = "Descriptive statistics of typically female tasks by Gender"
  , note = "This table was created with apa_table()."
  , escape = TRUE)
```

```{r, include=FALSE}
#descriptive_stats <- dat_reverse %>% group_by(gender) %>%
#  summarize(
#    Mean = mean(avg_housework_female)
#    , Median = median(avg_housework_female)
#    , SD = sd(avg_housework_female)
#    , Min = min(avg_housework_female)
#    , Max = max(avg_housework_female))
#descriptive_stats[, -1] <- printnum(descriptive_stats[, -1])
#apa_table(
#  descriptive_stats
#  , caption = "Descriptive statistics of typically female tasks by Gender"
#  , note = "This table was created with apa_table()."
#  , escape = TRUE)

```


```{r}
means <- dat_predyad%>%group_by(gender) %>%
  mutate(mean_housework_male = mean(avg_housework_male, na.rm = TRUE),
         mean_housework_female = mean(avg_housework_female, na.rm = TRUE),
         mean_grbs = mean(avg_grbs),
         gender = ifelse(gender == 0, "Male","Female"))%>%
  select(mean_housework_male,mean_housework_female,mean_grbs)
means <- means[c(1,2),]
apa_table(
  means
  , caption = "means"
  , note = "This table was created with apa_table()."
  , escape = TRUE)

```


# References

::: {#refs custom-style="Bibliography"}
:::
