---
title             : "Method Section: Measures and Descriptive Statistics Write-up"
shorttitle        : "housework analysis"

author: 
  - name          : "Carlotta Reinhardt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author

  - name          : "Margaret Bassney"
    affiliation   : "2"
    
   - name          : "Anushree Goswami"
    affiliation   : "3"


affiliation:
  - id            : "1"
    institution   : "Smith College"
  - id            : "2"
    institution   : "Smith College"
  - id            : "3"
    institution   : "Smith College"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Method
## Measures

- Scale used to measure each variable you intend to use
- Give the original variable name from the original dataset 
**partnum** Indicates the partner number. Each person was either partner 1 or partner 2.

**gender** Indicates the gender of the partner.
Variables:
Partner number (partnum) - 1 or 2
Gender (gender) - 0 or 1
Religion - text
Average Housework male - 0 to 100
Average housework female - 0 to 100
Average GRBS - 0 to 100
Housework Fair - 0 to 5
Housework Satisfied - 0 to 5 
Partner number 2 (partnum 2) - 1 or 
Relationship Length 




# Results
## Participant Demographics



\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
