---
title             : "Introduction"
shorttitle        : "housework and satisfaction"

author: 
  - name          : "Carlotta Reinhardt"
    affiliation   : "1"

  - name          : "Margaret Bassney"
    affiliation   : "1"

  - name          : "Anushree Goswami"
    affiliation   : "1"



affiliation:
  - id            : "1"
    institution   : "Smith College"


bibliography      : ["r-references.bib2"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

## Housework distribution and satisfaction: The moderating role of gender role beliefs and religion

Gender role beliefs have been widely debated in society for decades, as this controversial concept subjects men and women to gender-specific roles. One audible voice in this discourse is the voice of the Church. Pope Francis, for example, recently described gender theory as evil and dangerous because “[i]t would make everything homogeneous, neutral. It is an attack on difference, on the creativity of God and on men and women” [@catholic_league_pope_2020]. 

Traditionally, the majority of housework has been done by women while their male partners have been involved with paid labor. This distinction of gendered labor has been subject to the social change of the past few decades. Although most women in heterosexual couples are now as equally involved in paid labor as their male counterparts, they often still do the majority of the housework [@forste_fox_2008; @leopold_2019; @mikula_199]. 
(These evolving trends illustrate how traditional and conservative gender role beliefs are slowly becoming more liberal.)
Gender role beliefs still heavily influence women's role in society, from their job prospects to gender-based income inequalities. Even though men are now doing more housework than before the “gender revolution” [@goldschneider_2014], there is still an unequal housework distribution which has been found to result in lower satisfaction levels [@leopold_2019]. However, since past research [@forste_fox_2012; @baxter_western_1998] has shown that this relationship between housework distribution and satisfaction is complex, we will assess the extent to which two variables, religion and gender role beliefs, strengthen or dampen this relationship. 
(This will be done using a dyadic approach, which has not done before when assessing partner relationships.) - gap?
This research topic is important to investigate as it can help prevent future relationship conflicts and housework-related stress, which could impact negative health outcomes such as depressive symptoms, as well as divorce rates [@bird_99, @glass_fujimoto_94; @ruppanner_2012].
 

Numerous past studies have analyzed the growing relationship between housework distribution and satisfaction. @nelson_1977 found that almost half of the housewives in the sample were intrinsically satisfied, but did not explain why the satisfaction differed. Using data from the late 1900's, @baxter_western_1998 found that regardless of an extremely uneven distribution of housework labor, only 13-14% women were dissatisfied. In contrast, @mikula_1997 concluded that women did more housework than men and were significantly less satisfied. Their partners who performed less housework showed a higher satisfaction. More recent studies have found that women were more unsatisfied with the housework distribution than men and equal housework distribution was related to subjective marital equity [@charbonneau_2019; @spitze_loscocco_2000]. Therefore, it is not appropriate to assume that an equal distribution of housework labor is the only predictor of satisfaction. Specifically examining housework tasks, @ellison_bartkowski_2002 suggested that traditionally “female-typed” housework tasks have to be differentiated from “male-typed” tasks for a more accurate analysis of this relationship. “Female-typed” housework tasks include everyday chores such as laundry and cleaning. In most articles, the “female-typed” housework tasks were seen as prototypical housework tasks that significantly affected satisfaction levels [@benin_agostinelli_1988].


As outlined previously, although past research has shown contradictory findings regarding the relationship between housework distribution and satisfaction, the overall trend has been that women were found to be happier when they completed any amount of housework. @okulicz_valente_2018 proposed that this is currently changing because of the evolving gender role beliefs and the “gender revolution” [@goldschneider_2014]. Greater underbenefit, the act of one partner doing more housework than the other resulting in negative emotions, has been shown to relate to lower marital quality [@demaris_2010]. This notion of underbenefit contradicts past research in which female partners evaluated their uneven housework distribution in a positive way. A variable that can explain these inconsistent findings concerning housework distribution and satisfaction is gender role beliefs. Indeed, @buunk_2000, showed that egalitarian women tended to be more dissatisfied with an unequal distribution of housework in comparison to traditional women. Likewise, @evertson_2014 reported that people who held egalitarian gender role beliefs were more satisfied with a more equal distribution of housework. For egalitarian couples it was observed that housework was more equally distributed, while in households that held traditional views women still did the majority of the housework [@greenstein_1996]. This shows that couples strived towards a distribution of housework that satisfied them [@benin_agostinelli_1988], but this balance looked different for everyone. Researchers found that the highest satisfaction levels in traditional couples were when both partners had varying involvements in household tasks and the subjective incongruence between attitudes and behaviors regarding family roles was low [@forste_fox_2012]. It is therefore necessary to asses the effect of gender role beliefs on the relationship between housework distribution and satisfaction, as prior research suggests that this relationship could be reversed when comparing traditional and egalitarian couples.  

Men who were married to women with traditional views performed less housework than men who were married to women with egalitarian views [@greenstein_1996]. These men who did less housework were found to have greater satisfaction. This illustrates how gender role beliefs moderates the relationship between housework distribution and satisfaction, since the men who were married to women with higher gender role beliefs (traditional women) performed less housework and were therefore more satisfied. This unequal housework distribution can have severe health consequences, as a greater housework distribution has been associated with higher levels of depression [@glass_fujimoto_94]. Since prior research only focused on either the male or female partner, it did not provide a dyadic analysis on couples. This led to incomplete results which did not reveal all the information needed to fully understand underlying dynamics between these variables. Therefore, we will use a dyadic approach to assess this relationship.

Religion has been an important factor in relationship dynamics for decades. It provides a powerful framework for gender norms and beliefs that are sanctified and therefore qualitatively different from non-religious norms [@hunt_jung_2009]. For most religious denominations, religiosity was connected to patriarchal gender role attitudes at home [@goldschneider_2014]. As shown in the quote by pope Francis, religion and religious institutions are still powerful societal actors that influence intrinsic values and beliefs [@musek_2017]. Religion still continues to deeply impact the distribution of housework roles between heterosexual couples. Different levels of religiosity and different types of religions carry various gender role beliefs which shape the expectations of female and male responsibilities. Some common stereotypes and beliefs are that women should cook and clean, while men should perform paid labor and manage the car. However, while many couples have started to defy these stereotypes, some still follow this structure, especially if one partner strongly believes in them [@blair_lichter_1999]. In religious couples, even a small contribution towards housework from men was found to lead to higher female partner satisfaction [@demaris_2013]. 
- @gull_geist_2020 found that religion had a moderating effect on the type of housework task that religious men engage in.
- @ellison_bartkowski_2002 found religion to be a moderator on the amount of housework that the wife performs. 
Although previous studies suggested that religion, like gender role beliefs, has a moderating role, the actual impact of religion on the relationship between housework distribution and satisfaction has not been sufficiently investigated. 

In our study, we examined the relationship between housework distribution and satisfaction in a way past research has not done yet. This included a detailed investigation of the impact of the moderating factors, gender role beliefs and religion, and satisfaction of both partners. We conducted a questionnaire-based study that investigated the subjective housework distribution, satisfaction, religion, and gender role beliefs in heterosexual couples in a dyadic setting. We are interested in finding whether the relationship between housework distribution and satisfaction is moderated by gender role beliefs and religion, and 
(whether there are gender-related characteristics that affect one's own outcomes and their partner's outcomes.)
Based on prior research, we expect that the relationship between housework distribution and satisfaction is moderated by gender role beliefs. We hypothesize that the higher the amount of housework of an egalitarian partner, the lower the satisfaction is for an unequal housework distribution (Hypothesis 1a). For females with more traditional gender role beliefs, a reversed relationship is hypothesized. A higher amount of housework is associated with a higher level of satisfaction (Hypothesis 1b). Male partners with traditional gender role beliefs would be more satisfied if their wife did more housework (Hypothesis 1c). Because prior research lacks dyadic analyses, specifying the effects of each partners’ gender role beliefs on the relationship of interest will strengthen the current study. Similar to the moderating role of gender role beliefs, it is expected that because religion is connected to more traditional relationship ideals, it can be another moderator for the relationship between housework distribution and satisfaction. It is hypothesized that in non-religious couples, more housework is related to a lower satisfaction with housework distribution (Hypothesis 2a). For religious women, it is expected that more housework is connected to greater satisfaction (Hypothesis 2b) and religious male partners are more satisfied if their wife does more housework (Hypothesis 2c). 

Besides the hypothesized relationships described above, we will include an exploratory analysis on partner gatekeeping behaviors. Gatekeeping is defined as behaviors that prevent equal work performed by both partners in a relationship [@hawkins_1999]. According to @hawkins_1999, a mother's reluctance to share familial responsibility inhibits greater father involvement in family work, resulting in an unequal housework distribution. We will investigate whether gatekeeping in females is related to gender role beliefs and therefore mediates the relationship between housework distribution and satisfaction. Gatekeeping behaviors by one partner can shut out the other partner from performing a household task. 

This introduction was written in R [@R-base] with the papaja package [@R-papaja].


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
